Application of Network Flow and Linear Programming to Scheduling of Clinicians

### 2019-08-23 paper/tbl/2018_schedule_comparison.tex
Remove 2017 table + use adjustbox to scale table
Update plots and descriptions in results

% Table generated by Excel2LaTeX from sheet '2018'
\begin{table}[h]
	\tiny

@@

@@

    	                                                  &                  HIV                  &                                 ID                                 &                              Weekend                               &                  HIV                  &                                 ID                                 &                              Weekend                               \\ \midrule\midrule

@@

    	                        2                         & \cellcolor[rgb]{ .663,  .816,  .557}A &                \cellcolor[rgb]{ .957,  .69,  .518}E                &                \cellcolor[rgb]{ .518,  .592,  .69}G                & \cellcolor[rgb]{ .663,  .816,  .557}A &                \cellcolor[rgb]{ .957,  .69,  .518}E                &               \cellcolor[rgb]{ .663,  .816,  .557}A                \\

@@

    	                        7                         &   \cellcolor[rgb]{ 1,  .851,  .4}C    &               \cellcolor[rgb]{ .608,  .761,  .902}B                &                  \cellcolor[rgb]{ 1,  .851,  .4}C                  & \cellcolor[rgb]{ .663,  .816,  .557}A &               \cellcolor[rgb]{ .557,  .663,  .859}F                &               \cellcolor[rgb]{ .608,  .761,  .902}B                \\
    	                        8                         &   \cellcolor[rgb]{ 1,  .851,  .4}C    &               \cellcolor[rgb]{ .608,  .761,  .902}B                &                \cellcolor[rgb]{ .518,  .592,  .69}G                & \cellcolor[rgb]{ .788,  .788,  .788}D &                  \cellcolor[rgb]{ 1,  .851,  .4}C                  &                \cellcolor[rgb]{ .518,  .592,  .69}G                \\
    	                        9                         & \cellcolor[rgb]{ .788,  .788,  .788}D &               \cellcolor[rgb]{ .459,  .443,  .443}H                &               \cellcolor[rgb]{ .788,  .788,  .788}D                & \cellcolor[rgb]{ .608,  .761,  .902}B &                  \cellcolor[rgb]{ 1,  .851,  .4}C                  &               \cellcolor[rgb]{ .788,  .788,  .788}D                \\
    	                       10                         & \cellcolor[rgb]{ .788,  .788,  .788}D &               \cellcolor[rgb]{ .459,  .443,  .443}H                &               \cellcolor[rgb]{ .459,  .443,  .443}H                & \cellcolor[rgb]{ .608,  .761,  .902}B &               \cellcolor[rgb]{ .788,  .788,  .788}D                &               \cellcolor[rgb]{ .459,  .443,  .443}H                \\
    	                       11                         & \cellcolor[rgb]{ .663,  .816,  .557}A & \cellcolor[rgb]{ .251,  .251,  .251}\textcolor[rgb]{ 1,  1,  1}{I} & \cellcolor[rgb]{ .251,  .251,  .251}\textcolor[rgb]{ 1,  1,  1}{I} & \cellcolor[rgb]{ .663,  .816,  .557}A &               \cellcolor[rgb]{ .608,  .761,  .902}B                &               \cellcolor[rgb]{ .557,  .663,  .859}F                \\
    	                       12                         & \cellcolor[rgb]{ .663,  .816,  .557}A & \cellcolor[rgb]{ .251,  .251,  .251}\textcolor[rgb]{ 1,  1,  1}{I} &               \cellcolor[rgb]{ .608,  .761,  .902}B                & \cellcolor[rgb]{ .663,  .816,  .557}A &               \cellcolor[rgb]{ .608,  .761,  .902}B                &               \cellcolor[rgb]{ .663,  .816,  .557}A                \\
    	                       13                         & \cellcolor[rgb]{ .608,  .761,  .902}B &               \cellcolor[rgb]{ .557,  .663,  .859}F                &               \cellcolor[rgb]{ .557,  .663,  .859}F                &   \cellcolor[rgb]{ 1,  .851,  .4}C    &               \cellcolor[rgb]{ .459,  .443,  .443}H                &               \cellcolor[rgb]{ .459,  .443,  .443}H                \\
    	                       14                         & \cellcolor[rgb]{ .608,  .761,  .902}B &               \cellcolor[rgb]{ .557,  .663,  .859}F                &               \cellcolor[rgb]{ .459,  .443,  .443}H                &   \cellcolor[rgb]{ 1,  .851,  .4}C    &               \cellcolor[rgb]{ .459,  .443,  .443}H                & \cellcolor[rgb]{ .251,  .251,  .251}\textcolor[rgb]{ 1,  1,  1}{I} \\
    	                       15                         &   \cellcolor[rgb]{ 1,  .851,  .4}C    & \cellcolor[rgb]{ .251,  .251,  .251}\textcolor[rgb]{ 1,  1,  1}{I} &                  \cellcolor[rgb]{ 1,  .851,  .4}C                  & \cellcolor[rgb]{ .608,  .761,  .902}B & \cellcolor[rgb]{ .251,  .251,  .251}\textcolor[rgb]{ 1,  1,  1}{I} &                  \cellcolor[rgb]{ 1,  .851,  .4}C                  \\
    	                       16                         &   \cellcolor[rgb]{ 1,  .851,  .4}C    & \cellcolor[rgb]{ .251,  .251,  .251}\textcolor[rgb]{ 1,  1,  1}{I} &               \cellcolor[rgb]{ .663,  .816,  .557}A                & \cellcolor[rgb]{ .608,  .761,  .902}B & \cellcolor[rgb]{ .251,  .251,  .251}\textcolor[rgb]{ 1,  1,  1}{I} &                \cellcolor[rgb]{ .957,  .69,  .518}E                \\
    	                       17                         & \cellcolor[rgb]{ .608,  .761,  .902}B &               \cellcolor[rgb]{ .788,  .788,  .788}D                &               \cellcolor[rgb]{ .788,  .788,  .788}D                & \cellcolor[rgb]{ .663,  .816,  .557}A &                \cellcolor[rgb]{ .957,  .69,  .518}E                &               \cellcolor[rgb]{ .788,  .788,  .788}D                \\
    	                       18                         & \cellcolor[rgb]{ .608,  .761,  .902}B &               \cellcolor[rgb]{ .788,  .788,  .788}D                &               \cellcolor[rgb]{ .557,  .663,  .859}F                & \cellcolor[rgb]{ .663,  .816,  .557}A &                \cellcolor[rgb]{ .957,  .69,  .518}E                &                \cellcolor[rgb]{ .957,  .69,  .518}E                \\
    	                       19                         & \cellcolor[rgb]{ .663,  .816,  .557}A &               \cellcolor[rgb]{ .459,  .443,  .443}H                &               \cellcolor[rgb]{ .459,  .443,  .443}H                & \cellcolor[rgb]{ .663,  .816,  .557}A &                  \cellcolor[rgb]{ 1,  .851,  .4}C                  &               \cellcolor[rgb]{ .557,  .663,  .859}F                \\
    	                       20                         & \cellcolor[rgb]{ .663,  .816,  .557}A &               \cellcolor[rgb]{ .459,  .443,  .443}H                & \cellcolor[rgb]{ .251,  .251,  .251}\textcolor[rgb]{ 1,  1,  1}{I} & \cellcolor[rgb]{ .663,  .816,  .557}A &                  \cellcolor[rgb]{ 1,  .851,  .4}C                  &                  \cellcolor[rgb]{ 1,  .851,  .4}C                  \\
    	                       21                         & \cellcolor[rgb]{ .788,  .788,  .788}D &                  \cellcolor[rgb]{ 1,  .851,  .4}C                  &                  \cellcolor[rgb]{ 1,  .851,  .4}C                  & \cellcolor[rgb]{ .608,  .761,  .902}B &                \cellcolor[rgb]{ .518,  .592,  .69}G                &               \cellcolor[rgb]{ .663,  .816,  .557}A                \\
    	                       22                         & \cellcolor[rgb]{ .788,  .788,  .788}D &                  \cellcolor[rgb]{ 1,  .851,  .4}C                  &                \cellcolor[rgb]{ .518,  .592,  .69}G                & \cellcolor[rgb]{ .608,  .761,  .902}B &                \cellcolor[rgb]{ .518,  .592,  .69}G                &                  \cellcolor[rgb]{ 1,  .851,  .4}C                  \\
    	                       23                         & \cellcolor[rgb]{ .608,  .761,  .902}B &                \cellcolor[rgb]{ .957,  .69,  .518}E                &                \cellcolor[rgb]{ .957,  .69,  .518}E                &   \cellcolor[rgb]{ 1,  .851,  .4}C    &               \cellcolor[rgb]{ .557,  .663,  .859}F                &               \cellcolor[rgb]{ .788,  .788,  .788}D                \\
    	                       24                         & \cellcolor[rgb]{ .608,  .761,  .902}B &                \cellcolor[rgb]{ .957,  .69,  .518}E                &               \cellcolor[rgb]{ .557,  .663,  .859}F                &   \cellcolor[rgb]{ 1,  .851,  .4}C    &               \cellcolor[rgb]{ .557,  .663,  .859}F                &                  \cellcolor[rgb]{ 1,  .851,  .4}C                  \\

@@

    	                       27                         & \cellcolor[rgb]{ .608,  .761,  .902}B &                  \cellcolor[rgb]{ 1,  .851,  .4}C                  &                  \cellcolor[rgb]{ 1,  .851,  .4}C                  & \cellcolor[rgb]{ .663,  .816,  .557}A &               \cellcolor[rgb]{ .608,  .761,  .902}B                &                \cellcolor[rgb]{ .957,  .69,  .518}E                \\
    	                       28                         & \cellcolor[rgb]{ .608,  .761,  .902}B &                  \cellcolor[rgb]{ 1,  .851,  .4}C                  &                \cellcolor[rgb]{ .957,  .69,  .518}E                & \cellcolor[rgb]{ .663,  .816,  .557}A &               \cellcolor[rgb]{ .608,  .761,  .902}B                & \cellcolor[rgb]{ .251,  .251,  .251}\textcolor[rgb]{ 1,  1,  1}{I} \\
    	                       29                         & \cellcolor[rgb]{ .663,  .816,  .557}A &                \cellcolor[rgb]{ .518,  .592,  .69}G                &               \cellcolor[rgb]{ .663,  .816,  .557}A                & \cellcolor[rgb]{ .608,  .761,  .902}B &               \cellcolor[rgb]{ .788,  .788,  .788}D                &               \cellcolor[rgb]{ .788,  .788,  .788}D                \\
    	                       30                         & \cellcolor[rgb]{ .663,  .816,  .557}A &                \cellcolor[rgb]{ .518,  .592,  .69}G                &               \cellcolor[rgb]{ .608,  .761,  .902}B                & \cellcolor[rgb]{ .608,  .761,  .902}B &               \cellcolor[rgb]{ .788,  .788,  .788}D                &               \cellcolor[rgb]{ .663,  .816,  .557}A                \\
    	                       31                         &   \cellcolor[rgb]{ 1,  .851,  .4}C    &               \cellcolor[rgb]{ .557,  .663,  .859}F                &                  \cellcolor[rgb]{ 1,  .851,  .4}C                  &   \cellcolor[rgb]{ 1,  .851,  .4}C    &               \cellcolor[rgb]{ .557,  .663,  .859}F                &                \cellcolor[rgb]{ .957,  .69,  .518}E                \\
    	                       32                         &   \cellcolor[rgb]{ 1,  .851,  .4}C    &               \cellcolor[rgb]{ .557,  .663,  .859}F                &                \cellcolor[rgb]{ .957,  .69,  .518}E                &   \cellcolor[rgb]{ 1,  .851,  .4}C    &               \cellcolor[rgb]{ .557,  .663,  .859}F                &               \cellcolor[rgb]{ .557,  .663,  .859}F                \\

@@

    	                       34                         & \cellcolor[rgb]{ .608,  .761,  .902}B &               \cellcolor[rgb]{ .788,  .788,  .788}D                &               \cellcolor[rgb]{ .608,  .761,  .902}B                & \cellcolor[rgb]{ .608,  .761,  .902}B & \cellcolor[rgb]{ .251,  .251,  .251}\textcolor[rgb]{ 1,  1,  1}{I} &                  \cellcolor[rgb]{ 1,  .851,  .4}C                  \\
    	                       35                         & \cellcolor[rgb]{ .663,  .816,  .557}A & \cellcolor[rgb]{ .251,  .251,  .251}\textcolor[rgb]{ 1,  1,  1}{I} & \cellcolor[rgb]{ .251,  .251,  .251}\textcolor[rgb]{ 1,  1,  1}{I} & \cellcolor[rgb]{ .663,  .816,  .557}A &                \cellcolor[rgb]{ .518,  .592,  .69}G                &                \cellcolor[rgb]{ .518,  .592,  .69}G                \\

@@

    	                       37                         & \cellcolor[rgb]{ .788,  .788,  .788}D &                \cellcolor[rgb]{ .518,  .592,  .69}G                &               \cellcolor[rgb]{ .788,  .788,  .788}D                & \cellcolor[rgb]{ .788,  .788,  .788}D &                  \cellcolor[rgb]{ 1,  .851,  .4}C                  &               \cellcolor[rgb]{ .663,  .816,  .557}A                \\
    	                       38                         & \cellcolor[rgb]{ .788,  .788,  .788}D &                \cellcolor[rgb]{ .518,  .592,  .69}G                &               \cellcolor[rgb]{ .557,  .663,  .859}F                & \cellcolor[rgb]{ .788,  .788,  .788}D &               \cellcolor[rgb]{ .788,  .788,  .788}D                &                \cellcolor[rgb]{ .957,  .69,  .518}E                \\
    	                       39                         & \cellcolor[rgb]{ .663,  .816,  .557}A &                \cellcolor[rgb]{ .957,  .69,  .518}E                &               \cellcolor[rgb]{ .663,  .816,  .557}A                & \cellcolor[rgb]{ .663,  .816,  .557}A &               \cellcolor[rgb]{ .608,  .761,  .902}B                &               \cellcolor[rgb]{ .788,  .788,  .788}D                \\
    	                       40                         & \cellcolor[rgb]{ .663,  .816,  .557}A &                \cellcolor[rgb]{ .957,  .69,  .518}E                &               \cellcolor[rgb]{ .608,  .761,  .902}B                & \cellcolor[rgb]{ .608,  .761,  .902}B & \cellcolor[rgb]{ .251,  .251,  .251}\textcolor[rgb]{ 1,  1,  1}{I} & \cellcolor[rgb]{ .251,  .251,  .251}\textcolor[rgb]{ 1,  1,  1}{I} \\
    	                       41                         & \cellcolor[rgb]{ .608,  .761,  .902}B &                \cellcolor[rgb]{ .518,  .592,  .69}G                &                \cellcolor[rgb]{ .518,  .592,  .69}G                & \cellcolor[rgb]{ .608,  .761,  .902}B & \cellcolor[rgb]{ .251,  .251,  .251}\textcolor[rgb]{ 1,  1,  1}{I} &                \cellcolor[rgb]{ .518,  .592,  .69}G                \\
    	                       42                         & \cellcolor[rgb]{ .608,  .761,  .902}B &                \cellcolor[rgb]{ .518,  .592,  .69}G                &                \cellcolor[rgb]{ .957,  .69,  .518}E                & \cellcolor[rgb]{ .788,  .788,  .788}D &               \cellcolor[rgb]{ .557,  .663,  .859}F                &               \cellcolor[rgb]{ .557,  .663,  .859}F                \\
    	                       43                         & \cellcolor[rgb]{ .788,  .788,  .788}D &                  \cellcolor[rgb]{ 1,  .851,  .4}C                  &               \cellcolor[rgb]{ .788,  .788,  .788}D                &   \cellcolor[rgb]{ 1,  .851,  .4}C    &               \cellcolor[rgb]{ .557,  .663,  .859}F                &                  \cellcolor[rgb]{ 1,  .851,  .4}C                  \\
    	                       44                         & \cellcolor[rgb]{ .788,  .788,  .788}D &                  \cellcolor[rgb]{ 1,  .851,  .4}C                  & \cellcolor[rgb]{ .251,  .251,  .251}\textcolor[rgb]{ 1,  1,  1}{I} & \cellcolor[rgb]{ .788,  .788,  .788}D &                \cellcolor[rgb]{ .957,  .69,  .518}E                & \cellcolor[rgb]{ .251,  .251,  .251}\textcolor[rgb]{ 1,  1,  1}{I} \\
    	                       45                         & \cellcolor[rgb]{ .663,  .816,  .557}A &               \cellcolor[rgb]{ .557,  .663,  .859}F                &               \cellcolor[rgb]{ .557,  .663,  .859}F                & \cellcolor[rgb]{ .788,  .788,  .788}D &                \cellcolor[rgb]{ .957,  .69,  .518}E                &                \cellcolor[rgb]{ .957,  .69,  .518}E                \\
    	                       46                         & \cellcolor[rgb]{ .663,  .816,  .557}A &               \cellcolor[rgb]{ .557,  .663,  .859}F                &               \cellcolor[rgb]{ .663,  .816,  .557}A                & \cellcolor[rgb]{ .663,  .816,  .557}A &               \cellcolor[rgb]{ .608,  .761,  .902}B                &               \cellcolor[rgb]{ .663,  .816,  .557}A                \\
    	                       47                         &   \cellcolor[rgb]{ 1,  .851,  .4}C    &               \cellcolor[rgb]{ .608,  .761,  .902}B                &                  \cellcolor[rgb]{ 1,  .851,  .4}C                  & \cellcolor[rgb]{ .663,  .816,  .557}A &               \cellcolor[rgb]{ .608,  .761,  .902}B                &               \cellcolor[rgb]{ .788,  .788,  .788}D                \\
    	                       48                         &   \cellcolor[rgb]{ 1,  .851,  .4}C    &               \cellcolor[rgb]{ .608,  .761,  .902}B                & \cellcolor[rgb]{ .251,  .251,  .251}\textcolor[rgb]{ 1,  1,  1}{I} & \cellcolor[rgb]{ .663,  .816,  .557}A &               \cellcolor[rgb]{ .788,  .788,  .788}D                &                \cellcolor[rgb]{ .518,  .592,  .69}G                \\
    	                       49                         & \cellcolor[rgb]{ .663,  .816,  .557}A &               \cellcolor[rgb]{ .788,  .788,  .788}D                &               \cellcolor[rgb]{ .788,  .788,  .788}D                & \cellcolor[rgb]{ .663,  .816,  .557}A &               \cellcolor[rgb]{ .788,  .788,  .788}D                &               \cellcolor[rgb]{ .557,  .663,  .859}F                \\

>>>>

% Table generated by Excel2LaTeX from sheet '2018_oldLP'
\begin{table}[htbp]

@@

	\begin{adjustbox}{scale=0.8}

@@

          & HIV   & ID    & Weekend & HIV   & ID    & Weekend \\
    \midrule
    \midrule

@@

    2     & \cellcolor[rgb]{ .663,  .816,  .557}A & \cellcolor[rgb]{ .957,  .69,  .518}E & \cellcolor[rgb]{ .459,  .443,  .443}H & \cellcolor[rgb]{ .663,  .816,  .557}A & \cellcolor[rgb]{ .957,  .69,  .518}E & \cellcolor[rgb]{ .663,  .816,  .557}A \\

@@

    7     & \cellcolor[rgb]{ .608,  .761,  .902}B & \cellcolor[rgb]{ 1,  .851,  .4}C & \cellcolor[rgb]{ 1,  .851,  .4}C & \cellcolor[rgb]{ .663,  .816,  .557}A & \cellcolor[rgb]{ .557,  .663,  .859}F & \cellcolor[rgb]{ .608,  .761,  .902}B \\
    8     & \cellcolor[rgb]{ .608,  .761,  .902}B & \cellcolor[rgb]{ 1,  .851,  .4}C & \cellcolor[rgb]{ .518,  .592,  .69}G & \cellcolor[rgb]{ .788,  .788,  .788}D & \cellcolor[rgb]{ 1,  .851,  .4}C & \cellcolor[rgb]{ .518,  .592,  .69}G \\
    9     & \cellcolor[rgb]{ .788,  .788,  .788}D & \cellcolor[rgb]{ .251,  .251,  .251}\textcolor[rgb]{ 1,  1,  1}{I} & \cellcolor[rgb]{ .788,  .788,  .788}D & \cellcolor[rgb]{ .608,  .761,  .902}B & \cellcolor[rgb]{ 1,  .851,  .4}C & \cellcolor[rgb]{ .788,  .788,  .788}D \\
    10    & \cellcolor[rgb]{ .788,  .788,  .788}D & \cellcolor[rgb]{ .251,  .251,  .251}\textcolor[rgb]{ 1,  1,  1}{I} & \cellcolor[rgb]{ .459,  .443,  .443}H & \cellcolor[rgb]{ .608,  .761,  .902}B & \cellcolor[rgb]{ .788,  .788,  .788}D & \cellcolor[rgb]{ .459,  .443,  .443}H \\
    11    & \cellcolor[rgb]{ .663,  .816,  .557}A & \cellcolor[rgb]{ .608,  .761,  .902}B & \cellcolor[rgb]{ .608,  .761,  .902}B & \cellcolor[rgb]{ .663,  .816,  .557}A & \cellcolor[rgb]{ .608,  .761,  .902}B & \cellcolor[rgb]{ .557,  .663,  .859}F \\
    12    & \cellcolor[rgb]{ .663,  .816,  .557}A & \cellcolor[rgb]{ .608,  .761,  .902}B & \cellcolor[rgb]{ .251,  .251,  .251}\textcolor[rgb]{ 1,  1,  1}{I} & \cellcolor[rgb]{ .663,  .816,  .557}A & \cellcolor[rgb]{ .608,  .761,  .902}B & \cellcolor[rgb]{ .663,  .816,  .557}A \\
    13    & \cellcolor[rgb]{ 1,  .851,  .4}C & \cellcolor[rgb]{ .557,  .663,  .859}F & \cellcolor[rgb]{ .557,  .663,  .859}F & \cellcolor[rgb]{ 1,  .851,  .4}C & \cellcolor[rgb]{ .459,  .443,  .443}H & \cellcolor[rgb]{ .459,  .443,  .443}H \\
    14    & \cellcolor[rgb]{ 1,  .851,  .4}C & \cellcolor[rgb]{ .557,  .663,  .859}F & \cellcolor[rgb]{ .251,  .251,  .251}\textcolor[rgb]{ 1,  1,  1}{I} & \cellcolor[rgb]{ 1,  .851,  .4}C & \cellcolor[rgb]{ .459,  .443,  .443}H & \cellcolor[rgb]{ .251,  .251,  .251}\textcolor[rgb]{ 1,  1,  1}{I} \\
    15    & \cellcolor[rgb]{ .663,  .816,  .557}A & \cellcolor[rgb]{ .459,  .443,  .443}H & \cellcolor[rgb]{ .459,  .443,  .443}H & \cellcolor[rgb]{ .608,  .761,  .902}B & \cellcolor[rgb]{ .251,  .251,  .251}\textcolor[rgb]{ 1,  1,  1}{I} & \cellcolor[rgb]{ 1,  .851,  .4}C \\
    16    & \cellcolor[rgb]{ .663,  .816,  .557}A & \cellcolor[rgb]{ .459,  .443,  .443}H & \cellcolor[rgb]{ .788,  .788,  .788}D & \cellcolor[rgb]{ .608,  .761,  .902}B & \cellcolor[rgb]{ .251,  .251,  .251}\textcolor[rgb]{ 1,  1,  1}{I} & \cellcolor[rgb]{ .957,  .69,  .518}E \\
    17    & \cellcolor[rgb]{ .608,  .761,  .902}B & \cellcolor[rgb]{ .957,  .69,  .518}E & \cellcolor[rgb]{ .608,  .761,  .902}B & \cellcolor[rgb]{ .663,  .816,  .557}A & \cellcolor[rgb]{ .957,  .69,  .518}E & \cellcolor[rgb]{ .788,  .788,  .788}D \\
    18    & \cellcolor[rgb]{ .608,  .761,  .902}B & \cellcolor[rgb]{ .957,  .69,  .518}E & \cellcolor[rgb]{ .459,  .443,  .443}H & \cellcolor[rgb]{ .663,  .816,  .557}A & \cellcolor[rgb]{ .957,  .69,  .518}E & \cellcolor[rgb]{ .957,  .69,  .518}E \\
    19    & \cellcolor[rgb]{ .663,  .816,  .557}A & \cellcolor[rgb]{ .251,  .251,  .251}\textcolor[rgb]{ 1,  1,  1}{I} & \cellcolor[rgb]{ .251,  .251,  .251}\textcolor[rgb]{ 1,  1,  1}{I} & \cellcolor[rgb]{ .663,  .816,  .557}A & \cellcolor[rgb]{ 1,  .851,  .4}C & \cellcolor[rgb]{ .557,  .663,  .859}F \\
    20    & \cellcolor[rgb]{ .663,  .816,  .557}A & \cellcolor[rgb]{ .251,  .251,  .251}\textcolor[rgb]{ 1,  1,  1}{I} & \cellcolor[rgb]{ .788,  .788,  .788}D & \cellcolor[rgb]{ .663,  .816,  .557}A & \cellcolor[rgb]{ 1,  .851,  .4}C & \cellcolor[rgb]{ 1,  .851,  .4}C \\
    21    & \cellcolor[rgb]{ 1,  .851,  .4}C & \cellcolor[rgb]{ .788,  .788,  .788}D & \cellcolor[rgb]{ 1,  .851,  .4}C & \cellcolor[rgb]{ .608,  .761,  .902}B & \cellcolor[rgb]{ .518,  .592,  .69}G & \cellcolor[rgb]{ .663,  .816,  .557}A \\
    22    & \cellcolor[rgb]{ 1,  .851,  .4}C & \cellcolor[rgb]{ .788,  .788,  .788}D & \cellcolor[rgb]{ .251,  .251,  .251}\textcolor[rgb]{ 1,  1,  1}{I} & \cellcolor[rgb]{ .608,  .761,  .902}B & \cellcolor[rgb]{ .518,  .592,  .69}G & \cellcolor[rgb]{ 1,  .851,  .4}C \\
    23    & \cellcolor[rgb]{ .608,  .761,  .902}B & \cellcolor[rgb]{ .557,  .663,  .859}F & \cellcolor[rgb]{ .557,  .663,  .859}F & \cellcolor[rgb]{ 1,  .851,  .4}C & \cellcolor[rgb]{ .557,  .663,  .859}F & \cellcolor[rgb]{ .788,  .788,  .788}D \\
    24    & \cellcolor[rgb]{ .608,  .761,  .902}B & \cellcolor[rgb]{ .557,  .663,  .859}F & \cellcolor[rgb]{ .518,  .592,  .69}G & \cellcolor[rgb]{ 1,  .851,  .4}C & \cellcolor[rgb]{ .557,  .663,  .859}F & \cellcolor[rgb]{ 1,  .851,  .4}C \\

@@

    27    & \cellcolor[rgb]{ 1,  .851,  .4}C & \cellcolor[rgb]{ .788,  .788,  .788}D & \cellcolor[rgb]{ .788,  .788,  .788}D & \cellcolor[rgb]{ .663,  .816,  .557}A & \cellcolor[rgb]{ .608,  .761,  .902}B & \cellcolor[rgb]{ .957,  .69,  .518}E \\
    28    & \cellcolor[rgb]{ 1,  .851,  .4}C & \cellcolor[rgb]{ .788,  .788,  .788}D & \cellcolor[rgb]{ .957,  .69,  .518}E & \cellcolor[rgb]{ .663,  .816,  .557}A & \cellcolor[rgb]{ .608,  .761,  .902}B & \cellcolor[rgb]{ .251,  .251,  .251}\textcolor[rgb]{ 1,  1,  1}{I} \\
    29    & \cellcolor[rgb]{ .663,  .816,  .557}A & \cellcolor[rgb]{ .608,  .761,  .902}B & \cellcolor[rgb]{ .663,  .816,  .557}A & \cellcolor[rgb]{ .608,  .761,  .902}B & \cellcolor[rgb]{ .788,  .788,  .788}D & \cellcolor[rgb]{ .788,  .788,  .788}D \\
    30    & \cellcolor[rgb]{ .663,  .816,  .557}A & \cellcolor[rgb]{ .608,  .761,  .902}B & \cellcolor[rgb]{ .608,  .761,  .902}B & \cellcolor[rgb]{ .608,  .761,  .902}B & \cellcolor[rgb]{ .788,  .788,  .788}D & \cellcolor[rgb]{ .663,  .816,  .557}A \\
    31    & \cellcolor[rgb]{ 1,  .851,  .4}C & \cellcolor[rgb]{ .957,  .69,  .518}E & \cellcolor[rgb]{ 1,  .851,  .4}C & \cellcolor[rgb]{ 1,  .851,  .4}C & \cellcolor[rgb]{ .557,  .663,  .859}F & \cellcolor[rgb]{ .957,  .69,  .518}E \\
    32    & \cellcolor[rgb]{ 1,  .851,  .4}C & \cellcolor[rgb]{ .957,  .69,  .518}E & \cellcolor[rgb]{ .663,  .816,  .557}A & \cellcolor[rgb]{ 1,  .851,  .4}C & \cellcolor[rgb]{ .557,  .663,  .859}F & \cellcolor[rgb]{ .557,  .663,  .859}F \\

@@

    34    & \cellcolor[rgb]{ .608,  .761,  .902}B & \cellcolor[rgb]{ .788,  .788,  .788}D & \cellcolor[rgb]{ .957,  .69,  .518}E & \cellcolor[rgb]{ .608,  .761,  .902}B & \cellcolor[rgb]{ .251,  .251,  .251}\textcolor[rgb]{ 1,  1,  1}{I} & \cellcolor[rgb]{ 1,  .851,  .4}C \\
    35    & \cellcolor[rgb]{ .663,  .816,  .557}A & \cellcolor[rgb]{ .251,  .251,  .251}\textcolor[rgb]{ 1,  1,  1}{I} & \cellcolor[rgb]{ .663,  .816,  .557}A & \cellcolor[rgb]{ .663,  .816,  .557}A & \cellcolor[rgb]{ .518,  .592,  .69}G & \cellcolor[rgb]{ .518,  .592,  .69}G \\

@@

    37    & \cellcolor[rgb]{ .788,  .788,  .788}D & \cellcolor[rgb]{ 1,  .851,  .4}C & \cellcolor[rgb]{ 1,  .851,  .4}C & \cellcolor[rgb]{ .788,  .788,  .788}D & \cellcolor[rgb]{ 1,  .851,  .4}C & \cellcolor[rgb]{ .663,  .816,  .557}A \\
    38    & \cellcolor[rgb]{ .788,  .788,  .788}D & \cellcolor[rgb]{ 1,  .851,  .4}C & \cellcolor[rgb]{ .557,  .663,  .859}F & \cellcolor[rgb]{ .788,  .788,  .788}D & \cellcolor[rgb]{ .788,  .788,  .788}D & \cellcolor[rgb]{ .957,  .69,  .518}E \\
    39    & \cellcolor[rgb]{ .608,  .761,  .902}B & \cellcolor[rgb]{ .957,  .69,  .518}E & \cellcolor[rgb]{ .957,  .69,  .518}E & \cellcolor[rgb]{ .663,  .816,  .557}A & \cellcolor[rgb]{ .608,  .761,  .902}B & \cellcolor[rgb]{ .788,  .788,  .788}D \\
    40    & \cellcolor[rgb]{ .608,  .761,  .902}B & \cellcolor[rgb]{ .957,  .69,  .518}E & \cellcolor[rgb]{ .608,  .761,  .902}B & \cellcolor[rgb]{ .608,  .761,  .902}B & \cellcolor[rgb]{ .251,  .251,  .251}\textcolor[rgb]{ 1,  1,  1}{I} & \cellcolor[rgb]{ .251,  .251,  .251}\textcolor[rgb]{ 1,  1,  1}{I} \\
    41    & \cellcolor[rgb]{ .663,  .816,  .557}A & \cellcolor[rgb]{ .518,  .592,  .69}G & \cellcolor[rgb]{ .518,  .592,  .69}G & \cellcolor[rgb]{ .608,  .761,  .902}B & \cellcolor[rgb]{ .251,  .251,  .251}\textcolor[rgb]{ 1,  1,  1}{I} & \cellcolor[rgb]{ .518,  .592,  .69}G \\
    42    & \cellcolor[rgb]{ .663,  .816,  .557}A & \cellcolor[rgb]{ .518,  .592,  .69}G & \cellcolor[rgb]{ .957,  .69,  .518}E & \cellcolor[rgb]{ .788,  .788,  .788}D & \cellcolor[rgb]{ .557,  .663,  .859}F & \cellcolor[rgb]{ .557,  .663,  .859}F \\
    43    & \cellcolor[rgb]{ 1,  .851,  .4}C & \cellcolor[rgb]{ .251,  .251,  .251}\textcolor[rgb]{ 1,  1,  1}{I} & \cellcolor[rgb]{ 1,  .851,  .4}C & \cellcolor[rgb]{ 1,  .851,  .4}C & \cellcolor[rgb]{ .557,  .663,  .859}F & \cellcolor[rgb]{ 1,  .851,  .4}C \\
    44    & \cellcolor[rgb]{ 1,  .851,  .4}C & \cellcolor[rgb]{ .251,  .251,  .251}\textcolor[rgb]{ 1,  1,  1}{I} & \cellcolor[rgb]{ .251,  .251,  .251}\textcolor[rgb]{ 1,  1,  1}{I} & \cellcolor[rgb]{ .788,  .788,  .788}D & \cellcolor[rgb]{ .957,  .69,  .518}E & \cellcolor[rgb]{ .251,  .251,  .251}\textcolor[rgb]{ 1,  1,  1}{I} \\
    45    & \cellcolor[rgb]{ .663,  .816,  .557}A & \cellcolor[rgb]{ .557,  .663,  .859}F & \cellcolor[rgb]{ .663,  .816,  .557}A & \cellcolor[rgb]{ .788,  .788,  .788}D & \cellcolor[rgb]{ .957,  .69,  .518}E & \cellcolor[rgb]{ .957,  .69,  .518}E \\
    46    & \cellcolor[rgb]{ .663,  .816,  .557}A & \cellcolor[rgb]{ .557,  .663,  .859}F & \cellcolor[rgb]{ .557,  .663,  .859}F & \cellcolor[rgb]{ .663,  .816,  .557}A & \cellcolor[rgb]{ .608,  .761,  .902}B & \cellcolor[rgb]{ .663,  .816,  .557}A \\
    47    & \cellcolor[rgb]{ .608,  .761,  .902}B & \cellcolor[rgb]{ .518,  .592,  .69}G & \cellcolor[rgb]{ .608,  .761,  .902}B & \cellcolor[rgb]{ .663,  .816,  .557}A & \cellcolor[rgb]{ .608,  .761,  .902}B & \cellcolor[rgb]{ .788,  .788,  .788}D \\
    48    & \cellcolor[rgb]{ .608,  .761,  .902}B & \cellcolor[rgb]{ .518,  .592,  .69}G & \cellcolor[rgb]{ .251,  .251,  .251}\textcolor[rgb]{ 1,  1,  1}{I} & \cellcolor[rgb]{ .663,  .816,  .557}A & \cellcolor[rgb]{ .788,  .788,  .788}D & \cellcolor[rgb]{ .518,  .592,  .69}G \\
    49    & \cellcolor[rgb]{ .788,  .788,  .788}D & \cellcolor[rgb]{ 1,  .851,  .4}C & \cellcolor[rgb]{ .788,  .788,  .788}D & \cellcolor[rgb]{ .663,  .816,  .557}A & \cellcolor[rgb]{ .788,  .788,  .788}D & \cellcolor[rgb]{ .557,  .663,  .859}F \\
    50    & \cellcolor[rgb]{ .788,  .788,  .788}D & \cellcolor[rgb]{ 1,  .851,  .4}C & \cellcolor[rgb]{ .608,  .761,  .902}B & \cellcolor[rgb]{ .608,  .761,  .902}B & \cellcolor[rgb]{ .518,  .592,  .69}G & \cellcolor[rgb]{ .518,  .592,  .69}G \\
    51    & \cellcolor[rgb]{ .608,  .761,  .902}B & \cellcolor[rgb]{ .518,  .592,  .69}G & \cellcolor[rgb]{ .518,  .592,  .69}G & \cellcolor[rgb]{ .608,  .761,  .902}B & \cellcolor[rgb]{ .518,  .592,  .69}G & \cellcolor[rgb]{ .957,  .69,  .518}E \\
